---
title: "Phase one"
author: "Fan Gong"
date: "June 24, 2017"
output:
  github_document: default
---

#Preparation

Set work directory and install packages
```{r, warning=FALSE, message=FALSE}
library(lubridate)
library(ggplot2)
library(changepoint)
library(tsoutliers)
load("/Users/gongfan/Desktop/byteflow/Stock Market/complete_dataset.RData")
```

#First cycle
```{r,warning=FALSE}
#tail(rownames(df[df$date=="2014-12-30",]),1)
first_cycle <- df[1:108546,]
first_cycle$recv.time<- as.POSIXct(strptime(paste(first_cycle$date,first_cycle$recv.time),"%Y-%m-%d %H:%M:%S"))
ggplot(data = first_cycle, aes(x = recv.time,y = px)) + geom_line() 
```

##method 1 

I use the number of change points to represent the trend difference. 
```{r,warning=FALSE}
mvalue_first <- cpt.mean(first_cycle$px, method="PELT")
changepoint_first <- first_cycle[cpts(mvalue_first),]
head(changepoint_first)
plot(px~recv.time, data = first_cycle)
points(x=changepoint_first$recv.time, y=changepoint_first$px, col='red')
plot(mvalue_first)
```

*The result shows that during the signal day, it always has more change points.*

##method 2

I use the significance of dummy variable to show that there must be some trend differences between normal days and signal days.

###method 2 model
```{r,warning=FALSE}
first_cycle$sig <- "no"
first_cycle[first_cycle$date == "2014-12-19","sig"] <- "yes"
first_cycle$sig <- as.factor(first_cycle$sig)
lm1 <- lm(px~recv.time + sig, data = first_cycle) 
summary(lm1)
lm_without_dummy <- lm(px~recv.time, data = first_cycle)

plot(px~recv.time, data = first_cycle)
abline(lm1, col = "red")
abline(lm_without_dummy, col = "green")
legend("topright", legend = c('with dummy variable', 'without dummy variable'), col = c('red','green'), lty = 1)
```

###method 2 robust test 

suppose we randomly choose 10000 data points as signal days' data to test now whether or not the dummy variable is significant.
The reason I choose 10000 is because the signal day has 30000+ data.

```{r,warning=FALSE}
random_row <- base::sample(1:nrow(first_cycle), size = 10000)
first_cycle$sig <- "no"
first_cycle[random_row,"sig"] <- "yes"
first_cycle$sig <- as.factor(first_cycle$sig)
lm_robust <- lm(px~recv.time +sig, data = first_cycle)
summary(lm_robust)
```

*the output obviously shows that now the dummy variable is not statistical significant*




